Unifying Lower Bounds on Prediction Dimension of Consistent Convex Surrogates

### 2021-05-26 cvx-flats-neurips21/cvx-flats.tex
minor
3, 4

\subsection{Illustrating the condition in all four quadrants}
\label{sec:illustration}
We now illustrate how to apply Theorem~\ref{thm:convex-flats-inf-dim} to construct lower bounds on convex consistency dimension for targets across all four quadrants of Table~\ref{tab:quadrants}.
% by Corollaries~\ref{cor:Pcodim-flat-single-val-prop} (for continuous estimation problems; Q3, Q4) and~\ref{cor:Pcodim-flat-elic-relint-prop} (for discrete prediction problems; Q1, Q2).
% The illustrations in Figure~\ref{fig:quadrants-simplices} are simply intended to show how Lemma~\ref{lem:convex-flats-inf-dim} can be applied to results in all four quadrants of problem types-- making it the first lower bound to our knowledge to do so.
Throughout the examples, we will have $|\Y|=3$ so that the probability simplex can be visualized in two dimensions (Figure~\ref{fig:quadrants-simplices}).
For each, we take $d=1$, and thus ask whether a $1$-flat (a line in the figures) exists through the point $p$ while staying within the corresponding level set.

@@

To apply Theorem~\ref{thm:convex-flats-inf-dim}, we first consider the abstain property $\gamma$ elicited by $\ell^{1/2}$, where one predicts the most likely outcome $y$ if $Pr[Y=y] \geq 1/2$ and otherwise ``abstains'' by predicting $\bot$.
% Upon closer inspection, the level set boundaries are found at the set of distribution where is a $y$ such that $p_y = 1/2$.
For the depicted distribution $p \in \relint{\gamma_\bot}$, we can derive a lower bound on convex consistency dimension as we cannot fit a $1$-flat (line) fully contained in $\gamma_\bot$ that passes through $p$.
By Corollary~\ref{cor:Pcodim-flat-elic-relint-prop}, we can conclude $\conscvx(\gamma^{1/2}) \geq 2$ when $|\Y|=3$, which matches the upper bound from the convex surrogate of
\citet{ramaswamy2016convex}.\raft{Jessie: see if you can match the style of the revised abstain example for the others.  In particular, I think we can leave the definition of $p$ to the figure, and avoid referencing $\bullet$ or anything -- the figure can make clear that $p=\bullet$.  Probably it's only Q2 that needs to change. \jessie{Took a pass! Feel free to burn}}
%present a convex surrogate for the abstain loss yielding a logarithmic upper bound on $\conscvx(\ell^{1/2})$, so this bound is tight.% which are an exponential improvement over previous results, e.g.,~\citep{crammer2001algorithmic,rifkin2004defense}.

\paragraph{Q2: Variation of hierarchical classification.}
\jessiet{I don't like this phrasing, since it seems like we're pointing to Q1 then swerve to Q2}
\citet{ramaswamy2015hierarchical} studies a discrete target loss for hierarchical classification tasks~\citep{xiao2007hierarchical,burkhardt2005database}, such as the task in Figure~\ref{fig:hierarchical-tree}, in which one wishes to predict the deepest node in a tree that is ``likely enough.''
Consider the mild variation of this task where one wants to predict an outcome if it is likely enough, and otherwise proceed in a different direction and classify from another binary substructure as depicted in Figure~\ref{fig:quadrants-simplices} (Q2). 
Here, we take the reports and outcomes $\R = \Y$ to be the leaves of the tree in Figure~\ref{fig:hierarchical-tree}.
\citet{osband1985providing} notes that a property is elicitable if and only if its level sets form a power diagram projected onto the simplex, so there is no discrete target loss eliciting the described property, hence it belongs in Q2.

We can now model this problem by a property with the reports $\R = \Y$, and have 
\begin{align*}
\gamma(p) &= \begin{cases}
\text{active} & p_{\text{active}} \geq 1/2 \\
\text{median} & p_{\text{active}} \leq 1/2 \wedge p_{\text{median}} \geq p_{\text{passive}} \\
\text{passive} & p_{\text{active}} \leq 1/2 \wedge p_{\text{passive}} \geq p_{\text{median}} \\
\end{cases}~,~
\end{align*}

@@

In Figure~\ref{fig:quadrants-simplices} (Q2), we see that, like abstain, we cannot fit a $1$-flat (line) entirely contained in the level set $\gamma_{\text{passive}}$ through $p$.
Therefore, we can apply Theorem~\ref{thm:convex-flats-inf-dim} to conclude that $\conscvx(\gamma) = 2$.
\jessiet{Old narrative in comment}
%Consider the following scenario where someone is deciding how to dress for the weather based on a meteorologist's forecast: a forecaster is choosing between three outcomes $\Y = \{$rainy, sunny, snowy$\}$, and we suppose we want to have some bias towards health and safety, so the meteorologist should only predict sunny weather if $Pr[$sunny $|$ weather data$] \geq 3/4$.
%Otherwise, they should predict whatever is more likely  given the weather data: rain or snow.
%\citet{osband1985information-eliciting} notes that a property is elicitable if and only if its level sets form a power diagram projected onto the simplex, so there is no discrete target loss eliciting the described property, hence it belonging in Q2.
%
%We can now model this problem by a property with the reports $\R = \Y$, and have 
%\begin{align*}
%\gamma(p) &= \begin{cases}
%\text{sunny} & p_{\text{sunny}} \geq 1/2 \\
%\text{rainy} & p_{\text{sunny}} \leq 1/2 \wedge p_{\text{rainy}} \geq p_{\text{snowy}} \\
%\text{snowy} & p_{\text{sunny}} \leq 1/2 \wedge p_{\text{snowy}} \geq p_{\text{rainy}} \\
%\end{cases}~,~
%\end{align*} 
%
%This property is shown in Figure~\ref{fig:quadrants-simplices} (Q2), and we can observe the point that, like abstain, we cannot fit a $1$-flat (line) entirely contained in the level set $\gamma_{\text{snowy}}$ through $p$.
%Therefore, we can apply Theorem~\ref{thm:convex-flats-inf-dim} to conclude that $\conscvx(\gamma) = 2$.

\paragraph{Q3: Least-squares regression}
%\jessiet{Define property, discuss briefly why in the quadrant.  Move to how results apply and what they say}
While least squares regression is commonly used in machine learning and statistics for continuous estimation, it might not be immediately \emph{why} we do so, prompting us to study this smooth convex loss in Quadrant 3.
Evaluating the derivative of squared loss, we observe that it elicits the expected value $\Gamma(p) = \E_p[Y]$.
With $\Y = \{-1,0,1\}$, we can visualize the level sets of the expected value as in Figure~\ref{fig:quadrants-simplices} (Q3).
Since squared loss is a $1$-dimensional loss, we can verify that for all $p \in \simplex$, we can fit a $1$-flat (precisely equal to the level set) through $p$, as demonstrated in Figure~\ref{fig:quadrants-simplices}.

\paragraph{Q4: Variance}
One might reasonably want to estimate the variance $\Gamma^\Var(p) = \E_p[Y^2] - \E_p[Y]^2$, though a loss function to elicit the variance is not immediately obvious.
This property is continuous in $\simplex$, and therefore belongs in Quadrant 4.
The well-known fact that the variance is not elicitable does not yield a lower bound on elicitation complexity of 2, as it does not rule out the variance being a link of a real-valued convex-elicitable property; cf.~\citet[Remark 1]{frongillo2020elicitation}.
However, in Appendix~\ref{app:omitted-examples}, we show $\eliccvx(\Gamma^\Var)=2$, meaning the lowest dimension of a convex loss to estimate conditional variance is 2. %~\citep{osband1985providing,lambert2018elicitation}.
This lower bound will follow from Theorem~\ref{thm:bayes-risk-lower-bound} in Section~\ref{sec:contin-consis} using the fact that variance is the Bayes risk of squared loss $L(r,y) = (r-y)^2$, which elicits the mean $\Gamma(p) = \E_p Y$.
Interestingly, while perhaps intuitively obvious, even this simple result is novel.

\begin{SCfigure}
\begin{tabular}{c|c}
	%\hline
	\begin{tikzpicture} [scale=\tikzfigscale, thick, tdplot_main_coords]
	% standard tikz coordinate definition using x, y, z coords
	\coordinate (orig) at (0,0,0);

@@

	\begin{scope}
	\clip (h) -- (m) -- (l) -- (h);
	\draw[myblue] (1/2,1/2,0) -- (1/2, 0, 1/2);
	\draw[myblue] (0,1/2,1/2) -- (1/2, 0, 1/2);
	\draw[myblue] (0,1/2,1/2) -- (1/2,1/2, 0);
	\coordinate (point) at (0.3,0.4, 0.3);
	\draw[orange, dashed,shorten >= -3cm, shorten <=-3cm] (1/4,3/4,0) -- (point);
	\draw[orange, dashed,shorten >= -3cm, shorten <=-3cm] (0.7,0,0.3) -- (point);
	\node at (point) {$\bullet$};
	%\draw[orange, very thick] (0.7,0.3,0) -- (0.7,0.3,2);
	\end{scope}
	% \node[inner sep=2pt] (levset1) at (3/4,1/8,1/8) {$\gamma_{y_1}\!\!$};
	\node[inner sep=2pt] (levsetabs) at (5/12,5/12,1/6) {$\gamma_{\bot}$};
	%\draw[-latex,thin] (levset2) edge[in=270,out=90] (0.7,0.3,0);
	%\draw[-latex,thin] (levset1) edge[in=270,out=90] (0.3,0.7,0);
	\placefiglabel{(Q1)}
	\end{tikzpicture}
	&
	\begin{tikzpicture} [scale=\tikzfigscale, thick, tdplot_main_coords]
	% standard tikz coordinate definition using x, y, z coords
	\coordinate (orig) at (0,0,0);

@@

	\begin{scope}
	\clip (h) -- (m) -- (l) -- (h);
	\draw[myblue,thick] (1/2,0,1/2) -- (0,1/2, 1/2);
	\def\e{1/16};
	\draw[myblue,thick] (1/4,1/4,1/2) -- (1/2, 1/2, 0);
	\coordinate (point) at (0.3,0.4, 0.3);
	\draw[orange, dashed,shorten >= -3cm, shorten <=-3cm] (0.4, 0.6, 0.) -- (point);
	\draw[orange, dashed,shorten >= -3cm, shorten <=-3cm] (0,0.4,0.6) -- (point);
	\node at (point) {$\bullet$};
	%\draw[orange, very thick] (0.3,0.7,0) -- (0.3,0.7,2);
	%\draw[orange, very thick] (0.7,0.3,0) -- (0.7,0.3,2);
	\end{scope}
	% \node[inner sep=2pt] (levsetmin1) at (0.6, .2,.2) {$\gamma_{\text{passive}}$};
	\node[inner sep=2pt] (levset1) at (.2,0.6,.2) {$\gamma_{\text{median}}$};
	%\draw[-latex,thin] (levset2) edge[in=270,out=90] (0.7,0.3,0);
	%\draw[-latex,thin] (levset1) edge[in=270,out=90] (0.3,0.7,0);
	\placefiglabel{(Q2)}
	\end{tikzpicture}
	\\
	\hline
  \begin{tikzpicture} [scale=\tikzfigscale, thick, tdplot_main_coords]
% standard tikz coordinate definition using x, y, z coords
\coordinate (orig) at (0,0,0);

@@

\begin{scope}
\clip (h) -- (m) -- (l) -- (h);
\foreach \c in {0,0.05,...,1}
{
	\pgfmathsetmacro\aa{\c}
	\coordinate (A) at ($(\aa,1-\aa,0)$);
	\coordinate (B) at ($(\aa,1-\aa,2)$);
	\draw[myblue,thin] (A) -- (B);
}
\draw[myblue] (0.45,0.55,0) -- (0.45,.55,2);
\draw[myorange, very thick,dashed] (0.45,0.55,0) -- (0.45,.55,2);
%\draw[orange, very thick] (0.7,0.3,0) -- (0.7,0.3,2);
\end{scope}
\node (point) at (0.3,0.4,0.3) {$\bullet$};
\node[inner sep=2pt] (levset1) at (0.45,0.55, -0.3) {$\Gamma_{0.1}\!$};
%\node[inner sep=2pt] (levset2) at (0.7,0.3,-.3) {$\Gamma_{\!\!-0.4}\!\!\!\!$};
%\draw[-latex,thin] (levset2) edge[in=270,out=90] (0.7,0.3,0);
\draw[-latex,thin] (levset1) edge[in=270,out=90] (0.45,0.55,0);
\placefiglabel{(Q3)}
\end{tikzpicture}
&
\begin{tikzpicture} [scale=\tikzfigscale, thick, tdplot_main_coords]
% standard tikz coordinate definition using x, y, z coords
\coordinate (orig) at (0,0,0);

@@

\begin{scope}
\clip (h) -- (m) -- (l) -- (h);
\foreach \c in {0,0.1,...,1}
{
	\pgfmathsetmacro\aa{0.5*(sqrt(1-\c)+1)}
	\pgfmathsetmacro\bb{0.5*\c}
	\coordinate (A) at ($(\aa,1-\aa,0)$);
	\coordinate (B) at ($(1-\aa,\aa,0)$);
	\coordinate (C) at ($(\bb,\bb,1-2*\bb)$);
	\draw[myblue,thin] (C) parabola (A);
	\draw[myblue,thin] (C) parabola (B);
}
\def\c{0.6}
\pgfmathsetmacro\aa{0.5*(sqrt(1-\c)+1)}
\pgfmathsetmacro\bb{0.5*\c}
\coordinate (A) at ($(\aa,1-\aa,0)$);
\coordinate (B) at ($(1-\aa,\aa,0)$);
\coordinate (C) at ($(\bb,\bb,1-2*\bb)$);
\coordinate (Cleft) at ($(\bb + 2,\bb,1-2*\bb)$);
\coordinate (Cright) at ($(\bb,\bb + 2,1-2*\bb)$);
\coordinate (centerdot) at (0.21,0.445, 0.345);
\draw[myblue, very thick] (C) parabola (A);
\draw[myblue, very thick] (C) parabola (B);
\draw[orange, dashed,shorten >= -3cm, shorten <=-3cm] (1/10,9/10,0) -- (centerdot);
\node at (centerdot) {$\bullet$};
\end{scope}
\def\c{0.6}
\pgfmathsetmacro\aa{0.5*(sqrt(1-\c)+1)}
\pgfmathsetmacro\bb{0.5*\c}
\node[inner sep=2pt] (levset1) at (0.45,0.55, -0.3) {\vphantom{$\Gamma_{0.1}$}};
\node (levset) at (0.5,0.5,-.15) {$\Gamma_{0.6}$};
\draw[-latex,thin] (levset) edge[in=330,out=180] ($(\aa,1-\aa,0)$);
\draw[-latex,thin] (levset) edge[in=210,out=0] ($(1-\aa,\aa,0)$);
\placefiglabel{(Q4)}
\end{tikzpicture}
%\\
%\hline
\end{tabular}
\caption{Example properties for each quadrant. 
Throughout, we take $\bullet$ to be the distribution $p = (0.3, 0.3, 0.4)$ according to the left, top, and right outcomes respectively. 
(Q1,Q2) We cannot fit a $1$-flat (line) through $p$ without leaving the level sets $\gamma_\bot$ and $\gamma_{\text{median}}$, respectively;
Theorem~\ref{thm:convex-flats-inf-dim} implies that there is no $1$-dimensional consistent convex surrogate for either problem.
(Q3) Squared error is a $1$-dimensional convex loss, and indeed it elicits the mean of $Y$, whose level sets are all $1$-flats.
(Q4) The level sets of the variance are curved and cannot fit a $1$-flat; from Theorem~\ref{thm:convex-flats-inf-dim} there is no $1$-dimensional convex surrogate consistent for the variance.
\raf{Tweaked the fig, FYI: removed some level set labels, changed $\Gamma_{0.05}$ to $\Gamma_{0.1}$ in Q3}
}\label{fig:quadrants-simplices}
\end{SCfigure}

\subsection{Breadth of framework: Discrete-valued predictions}\label{sec:discrete-predictions-refactored}

@@

Theorem~\ref{thm:convex-flats-inf-dim} subsumes the  bounds given by~\citet{ramaswamy2016convex} by showing that, if there is a $d$-flat fully contained in the level set (so we can apply Theorem~\ref{thm:convex-flats-inf-dim}) then the co-dimension of the subspace of feasible directions at the same $p \in \C := \gamma_r$ has co-dimension at most $d$.

@@

In other words, any $d$-flat through $p$ is a subspace of feasible directions of co-dimension at most $d$, so Theorem~\ref{thm:convex-flats-inf-dim} provides a weakly tighter lower bound on convex consistency dimension than~\citet[Theorem 16]{ramaswamy2016convex}.
In Appendix~\ref{sec:finite-calib}, we show examples where the $d$-flats bound both matches the feasible subspace dimension bound and strictly improves it in order to emphasize that our result is strictly broader than previous bounds for Quadrant 1 from~\citet{ramaswamy2016convex}.

The feasible subspace dimension bound uses ``local'' information of the property to construct lower bounds, while $d$-flats in Theorem~\ref{thm:convex-flats-inf-dim} allow us to also use ``global'' information, while subsuming the previous results about local information.

@@

%commented out Jun 1 2020
%Theorem~\ref{thm:consistent-implies-indir-elic} allows us to use convex elicitation complexity as a tool to understand efficiency of consistent convex surrogates for a given property, which is more often what is given in a continuous estimation setting.
%For example, when one wants to learn an $\alpha$-quantile, we start with the property rather than a loss.
%In the literature, pinball loss $L(r,y) = (r-y)(\ones_{r \geq y} - \alpha)$ typically appears without explanation or justification as to why it is relevant in relation to the $\alpha$-quantile.
%Elicitation teaches us why pinball loss is consistent for learning a quantile as the pinball loss elicits the $\alpha$-quantile.
In continuous estimation problems, often one is not given a target loss, but instead a target (conditional) statistic of the data one wishes to estimate.
Examples include estimating the mean or variance of $y$ conditioned on a given $x$.
In this setting, Theorem~\ref{thm:convex-flats-inf-dim} gives lower bounds on the prediction dimension of convex losses with a link to the desired conditional statistic, i.e., the convex elicitation complexity.
In particular,
% following an argument from~\citet{frongillo2020elicitation},
Theorem~\ref{thm:bayes-risk-lower-bound} below yields new bounds on the convex elicitation complexity of statistics which quantify risk or uncertainty such as variance, entropy, or financial risk measures.

>>>>

\subsection{Illustrating the condition in all four quadrants}
\label{sec:illustration}
We now illustrate how to apply Theorem~\ref{thm:convex-flats-inf-dim} to construct lower bounds on convex consistency dimension for targets across all four quadrants of Table~\ref{tab:quadrants}.
% by Corollaries~\ref{cor:Pcodim-flat-single-val-prop} (for continuous estimation problems; Q3, Q4) and~\ref{cor:Pcodim-flat-elic-relint-prop} (for discrete prediction problems; Q1, Q2).
% The illustrations in Figure~\ref{fig:quadrants-simplices} are simply intended to show how Lemma~\ref{lem:convex-flats-inf-dim} can be applied to results in all four quadrants of problem types-- making it the first lower bound to our knowledge to do so.
Throughout the examples, we will have $|\Y|=3$ so that the probability simplex can be visualized in two dimensions (Figure~\ref{fig:quadrants-simplices}).
For each, we take $d=1$, and thus ask whether any $1$-flat (a line in the figures) passes through the point $p$ while staying within the corresponding level set.

@@

To apply Theorem~\ref{thm:convex-flats-inf-dim}, we first consider the abstain property $\gamma$ elicited by $\ell^{1/2}$, where one predicts the most likely outcome $y$ if $Pr[Y=y] \geq 1/2$ and otherwise ``abstains'' by predicting $\bot$.
% Upon closer inspection, the level set boundaries are found at the set of distribution where is a $y$ such that $p_y = 1/2$.
For the depicted distribution $p \in \relint{\gamma_\bot}$, we cannot fit a $1$-flat (line) fully contained in $\gamma_\bot$ that passes through $p$.
By Corollary~\ref{cor:Pcodim-flat-elic-relint-prop}, we can conclude $\conscvx(\gamma^{1/2}) \geq 2$ when $|\Y|=3$, meaning there is no consistent convex surrogate in 1 dimension.
This lower bound matches the upper bound from the convex surrogate of
\citet{ramaswamy2016convex}.

\paragraph{Q2: Variation of hierarchical classification.}
\jessiet{I don't like this phrasing, since it seems like we're pointing to Q1 then swerve to Q2}
\raft{Good point; reworded}
\citet{ramaswamy2015hierarchical} study hierarchical classification tasks, in which labels are arranged in a tree and one wishes to predict the deepest node in a tree that is ``likely enough'' \citep{xiao2007hierarchical,burkhardt2005database}.
Consider the variation of this task where one can only predict leaves of this tree.
For example, Figure~\ref{fig:hierarchical-tree} depicts a speech classification task where speech is either active or non-active, and non-active is further subdivided into median and passive.
It is natural to predict active if that label is more likely than both non-active labels combined, and otherwise to predict the most likely of median and passive:
\begin{align*}
\gamma(p) &= \begin{cases}
\text{active} & p_{\text{active}} \geq 1/2 \\
\text{median} & p_{\text{active}} \leq 1/2 \wedge p_{\text{median}} \geq p_{\text{passive}} \\
\text{passive} & p_{\text{active}} \leq 1/2 \wedge p_{\text{passive}} \geq p_{\text{median}} \\
\end{cases}~.
\end{align*} 
This ``T-shaped'' property is depicted in Figure~\ref{fig:quadrants-simplices} (Q2).
This task falls under Quadrant 2, as this property is not elicited by any target loss.%
\footnote{The cells of every finite elicitable property form a power diagram, which disallow this ``T-shaped'' configuration~\cite{lambert2009eliciting,frongillo2014general}.}
Like abstain, we cannot fit a $1$-flat (line) entirely contained in the level set $\gamma_{\text{passive}}$ through the depicted $p$, so Theorem~\ref{thm:convex-flats-inf-dim} again gives $\conscvx(\gamma) = 2$.

@@

\jessiet{Old narrative in comment}
%Consider the following scenario where someone is deciding how to dress for the weather based on a meteorologist's forecast: a forecaster is choosing between three outcomes $\Y = \{$rainy, sunny, snowy$\}$, and we suppose we want to have some bias towards health and safety, so the meteorologist should only predict sunny weather if $Pr[$sunny $|$ weather data$] \geq 3/4$.
%Otherwise, they should predict whatever is more likely  given the weather data: rain or snow.
%\citet{osband1985information-eliciting} notes that a property is elicitable if and only if its level sets form a power diagram projected onto the simplex, so there is no discrete target loss eliciting the described property, hence it belonging in Q2.
%
%We can now model this problem by a property with the reports $\R = \Y$, and have 
%\begin{align*}
%\gamma(p) &= \begin{cases}
%\text{sunny} & p_{\text{sunny}} \geq 1/2 \\
%\text{rainy} & p_{\text{sunny}} \leq 1/2 \wedge p_{\text{rainy}} \geq p_{\text{snowy}} \\
%\text{snowy} & p_{\text{sunny}} \leq 1/2 \wedge p_{\text{snowy}} \geq p_{\text{rainy}} \\
%\end{cases}~,~
%\end{align*} 
%
%This property is shown in Figure~\ref{fig:quadrants-simplices} (Q2), and we can observe the point that, like abstain, we cannot fit a $1$-flat (line) entirely contained in the level set $\gamma_{\text{snowy}}$ through $p$.
%Therefore, we can apply Theorem~\ref{thm:convex-flats-inf-dim} to conclude that $\conscvx(\gamma) = 2$.

\paragraph{Q3: Least-squares regression}
% \jessiet{Define property, discuss briefly why in the quadrant.  Move to how results apply and what they say}
Squared loss is commonly used in machine learning and statistics for continuous estimation, making it the canonical choice for Quadrant 3.
Squared loss is a $1$-dimensional convex loss which elicits the mean $\Gamma(p) = \E_p[Y]$.
Theorem~\ref{thm:convex-flats-inf-dim} therefore states that we can fit a $1$-flat through any distribution $p$ while staying within the corresponding level set.
In fact, the level sets of the mean are all exactly $1$-flats, as demonstrated in Figure~\ref{fig:quadrants-simplices} (Q3).

\paragraph{Q4: Variance}
Consider the task of estimating the variance $\Gamma^\Var(p) = \E_p[Y^2] - \E_p[Y]^2$.
Interestingly, the variance is not elicitable as its level sets are not convex~\cite{osband1985providing,lambert2008eliciting}, meaning this task falls under Quadrant 4.
The fact that the variance is not elicitable does not yield a lower bound on elicitation complexity of 2, as it does not rule out the variance being a link of a real-valued convex-elicitable property; cf.~\citet[Remark 1]{frongillo2020elicitation}.
In Appendix~\ref{app:omitted-examples}, we show $\eliccvx(\Gamma^\Var)=2$, meaning the lowest dimension of a convex loss to estimate conditional variance is 2. %~\citep{osband1985providing,lambert2018elicitation}.
This lower bound will follow from Theorem~\ref{thm:bayes-risk-lower-bound} in Section~\ref{sec:contin-consis} using the fact that variance is the Bayes risk of squared loss. % $L(r,y) = (r-y)^2$, which elicits the mean $\Gamma(p) = \E_p Y$.
Interestingly, while perhaps intuitively obvious, even this simple result is novel.

\begin{SCfigure}
  \begin{tabular}{c|c}
    % \hline
    \hspace*{-10pt}
    \begin{tikzpicture} [scale=\tikzfigscale, thick, tdplot_main_coords]
      % standard tikz coordinate definition using x, y, z coords
      \coordinate (orig) at (0,0,0);

@@

      \begin{scope}
	\clip (h) -- (m) -- (l) -- (h);
	\draw[myblue] (1/2,1/2,0) -- (1/2, 0, 1/2);
	\draw[myblue] (0,1/2,1/2) -- (1/2, 0, 1/2);
	\draw[myblue] (0,1/2,1/2) -- (1/2,1/2, 0);
	\coordinate (point) at (0.3,0.4, 0.3);
	\draw[orange, dashed,shorten >= -3cm, shorten <=-3cm] (1/4,3/4,0) -- (point);
	\draw[orange, dashed,shorten >= -3cm, shorten <=-3cm] (0.7,0,0.3) -- (point);
	\node at (point) {$\bullet$};
	% \draw[orange, very thick] (0.7,0.3,0) -- (0.7,0.3,2);
      \end{scope}
      % \node[inner sep=2pt] (levset1) at (3/4,1/8,1/8) {$\gamma_{y_1}\!\!$};
      \node[inner sep=2pt] (levsetabs) at (5/12,5/12,1/6) {$\gamma_{\bot}$};
      % \draw[-latex,thin] (levset2) edge[in=270,out=90] (0.7,0.3,0);
      % \draw[-latex,thin] (levset1) edge[in=270,out=90] (0.3,0.7,0);
      \placefiglabel{(Q1)}
    \end{tikzpicture}
    &
      \begin{tikzpicture} [scale=\tikzfigscale, thick, tdplot_main_coords]
	% standard tikz coordinate definition using x, y, z coords
	\coordinate (orig) at (0,0,0);

@@

	\begin{scope}
          \clip (h) -- (m) -- (l) -- (h);
          \draw[myblue,thick] (1/2,0,1/2) -- (0,1/2, 1/2);
          \def\e{1/16};
          \draw[myblue,thick] (1/4,1/4,1/2) -- (1/2, 1/2, 0);
          \coordinate (point) at (0.3,0.4, 0.3);
          \draw[orange, dashed,shorten >= -3cm, shorten <=-3cm] (0.4, 0.6, 0.) -- (point);
          \draw[orange, dashed,shorten >= -3cm, shorten <=-3cm] (0,0.4,0.6) -- (point);
          \node at (point) {$\bullet$};
          % \draw[orange, very thick] (0.3,0.7,0) -- (0.3,0.7,2);
          % \draw[orange, very thick] (0.7,0.3,0) -- (0.7,0.3,2);
	\end{scope}
	% \node[inner sep=2pt] (levsetmin1) at (0.6, .2,.2) {$\gamma_{\text{passive}}$};
	\node[inner sep=2pt] (levset1) at (.2,0.6,.2) {$\gamma_{\text{median}}$};
	% \draw[-latex,thin] (levset2) edge[in=270,out=90] (0.7,0.3,0);
	% \draw[-latex,thin] (levset1) edge[in=270,out=90] (0.3,0.7,0);
	\placefiglabel{(Q2)}
      \end{tikzpicture}
      \hspace*{-10pt}
    \\
    \hline
    \hspace*{-10pt}
    \begin{tikzpicture} [scale=\tikzfigscale, thick, tdplot_main_coords]
      % standard tikz coordinate definition using x, y, z coords
      \coordinate (orig) at (0,0,0);

@@

      \begin{scope}
        \clip (h) -- (m) -- (l) -- (h);
        \foreach \c in {0,0.05,...,1}
        {
          \pgfmathsetmacro\aa{\c}
          \coordinate (A) at ($(\aa,1-\aa,0)$);
          \coordinate (B) at ($(\aa,1-\aa,2)$);
          \draw[myblue,thin] (A) -- (B);
        }
        \draw[myblue] (0.45,0.55,0) -- (0.45,.55,2);
        \draw[myorange, very thick,dashed] (0.45,0.55,0) -- (0.45,.55,2);
        % \draw[orange, very thick] (0.7,0.3,0) -- (0.7,0.3,2);
      \end{scope}
      \node (point) at (0.3,0.4,0.3) {$\bullet$};
      \node[inner sep=2pt] (levset1) at (0.45,0.55, -0.3) {$\Gamma_{0.1}\!$};
      % \node[inner sep=2pt] (levset2) at (0.7,0.3,-.3) {$\Gamma_{\!\!-0.4}\!\!\!\!$};
      % \draw[-latex,thin] (levset2) edge[in=270,out=90] (0.7,0.3,0);
      \draw[-latex,thin] (levset1) edge[in=270,out=90] (0.45,0.55,0);
      \placefiglabel{(Q3)}
    \end{tikzpicture}
    &
      \begin{tikzpicture} [scale=\tikzfigscale, thick, tdplot_main_coords]
        % standard tikz coordinate definition using x, y, z coords
        \coordinate (orig) at (0,0,0);

@@

        \begin{scope}
          \clip (h) -- (m) -- (l) -- (h);
          \foreach \c in {0,0.1,...,1}
          {
            \pgfmathsetmacro\aa{0.5*(sqrt(1-\c)+1)}
            \pgfmathsetmacro\bb{0.5*\c}
            \coordinate (A) at ($(\aa,1-\aa,0)$);
            \coordinate (B) at ($(1-\aa,\aa,0)$);
            \coordinate (C) at ($(\bb,\bb,1-2*\bb)$);
            \draw[myblue,thin] (C) parabola (A);
            \draw[myblue,thin] (C) parabola (B);
          }
          \def\c{0.6}
          \pgfmathsetmacro\aa{0.5*(sqrt(1-\c)+1)}
          \pgfmathsetmacro\bb{0.5*\c}
          \coordinate (A) at ($(\aa,1-\aa,0)$);
          \coordinate (B) at ($(1-\aa,\aa,0)$);
          \coordinate (C) at ($(\bb,\bb,1-2*\bb)$);
          \coordinate (Cleft) at ($(\bb + 2,\bb,1-2*\bb)$);
          \coordinate (Cright) at ($(\bb,\bb + 2,1-2*\bb)$);
          \coordinate (centerdot) at (0.21,0.445, 0.345);
          \draw[myblue, very thick] (C) parabola (A);
          \draw[myblue, very thick] (C) parabola (B);
          \draw[orange, dashed,shorten >= -3cm, shorten <=-3cm] (1/10,9/10,0) -- (centerdot);
          \node at (centerdot) {$\bullet$};
        \end{scope}
        \def\c{0.6}
        \pgfmathsetmacro\aa{0.5*(sqrt(1-\c)+1)}
        \pgfmathsetmacro\bb{0.5*\c}
        \node[inner sep=2pt] (levset1) at (0.45,0.55, -0.3) {\vphantom{$\Gamma_{0.1}$}};
        \node (levset) at (0.5,0.5,-.15) {$\Gamma_{0.6}$};
        \draw[-latex,thin] (levset) edge[in=330,out=180] ($(\aa,1-\aa,0)$);
        \draw[-latex,thin] (levset) edge[in=210,out=0] ($(1-\aa,\aa,0)$);
        \placefiglabel{(Q4)}
      \end{tikzpicture}
      \hspace*{-10pt}
      % \\
      % \hline
  \end{tabular}
\caption{Example properties for each quadrant. 
Throughout, we take $\bullet$ to be the distribution $p = (0.3, 0.3, 0.4)$ according to the left, top, and right outcomes respectively. 
(Q1,Q2) We cannot fit a $1$-flat (line) through $p$ without leaving the level sets $\gamma_\bot$ and $\gamma_{\text{median}}$, respectively;
Theorem~\ref{thm:convex-flats-inf-dim} implies that there is no $1$-dimensional consistent convex surrogate for either problem.
(Q3) Squared error is a $1$-dimensional convex loss, and indeed it elicits the mean of $Y$, whose level sets are all $1$-flats.
(Q4) The level sets of the variance are curved and cannot fit a $1$-flat; from Theorem~\ref{thm:convex-flats-inf-dim} there is no $1$-dimensional convex surrogate consistent for the variance.
\raf{FYI: removed some level set labels, changed $\Gamma_{0.05}$ to $\Gamma_{0.1}$ in Q3}
}\label{fig:quadrants-simplices}
\end{SCfigure}

\subsection{Relation to feasible subspace dimension}\label{sec:discrete-predictions-refactored}

@@

Theorem~\ref{thm:convex-flats-inf-dim} subsumes the  bounds given by~\citet{ramaswamy2016convex} by showing that, if there is a $d$-flat through $p$ fully contained in a level set $\gamma_r$ (so we can apply Theorem~\ref{thm:convex-flats-inf-dim}) then the subspace of feasible directions at the same $p \in \C := \gamma_r$ has co-dimension at most $d$.

@@

In other words, any $d$-flat through $p$ is a subspace of feasible directions of co-dimension at most $d$, so Theorem~\ref{thm:convex-flats-inf-dim} provides a weakly tighter lower bound on convex consistency dimension than~\citet[Theorem 16]{ramaswamy2016convex}.
In fact, the $d$-flats bound can be strictly tighter; in Appendix~\ref{sec:finite-calib} we show that the abstain example from Figure~\ref{fig:quadrants-simplices} (Q1) yields a $d$-flats lower bound of 2 and a feasible subspace dimension lower bound of 1.
This gap stems from the fact that feasible subspace dimension uses only local information of the property to construct lower bounds, while $d$-flats in Theorem~\ref{thm:convex-flats-inf-dim} allow us to additionally use global information.
See Figure~\ref{fig:fsd-flats-abstain} in Appendix~\ref{sec:finite-calib} for an illustration.

@@

\raf{New intro... something along these lines}

We now turn to two main applications of Theorem~\ref{thm:convex-flats-inf-dim}: new lower bounds on the convex consistency dimension of risk measures (\S~\ref{sec:risk-measures}), and the mode and modal interval (\S~\ref{sec:mode-modal-interval}).
In both cases, we build on previous results due to \citet{frongillo2020elicitation} and \citet{dearborn2020indirect} which showed lower bounds with respect to \emph{identifiable} properties;
a property is $d$-identifiable if its level sets are all $d$-flats, as in Figure~\ref{fig:quadrants-simplices} (Q3).
In contrast, properties elicited by non-smooth convex losses are generally not identifiable.
For example, the properties elicited by hinge loss and the abstain surrogate are not identifiable, as their level sets are not flats; see Figure~\ref{fig:quadrants-simplices} (Q1).
It therefore might appear that entirely new ideas are needed.
Indeed, both papers above pose developing similar bounds with respect to convex-elicitable properties as a major open question.

Using our framework, we establish such bounds, resolving both open questions.
The central observation, from Theorem~\ref{thm:convex-flats-inf-dim}, is that the level sets of $d$-dimensional convex-elicitable properties, if not $d$-flats themselves, are \emph{unions} of $d$-flats.
Using this observation, we can modify the arguments of~\citet{frongillo2020elicitation} and~\citet{dearborn2020indirect} to give similar bounds.
In all cases, our lower bounds match the identifiable case, though we conjecture they are not tight in all cases.

\raf{MOVE}
